---
title: "Milestone_2_Final_Project"
author: "Prerna Sehgal"
date: "11/21/2019"
output: html_document
---

## R Markdown

## Proposed Analysis
I want to look at binding pattern differences between the WT and mutant Runx2.
For this I have four questions that I want to answer:
1. What regulatory elements are bound by the WT and the mutant?
2. Runx2 WT and mutant binding to TSS regions?
3. How is the enrichment of the protein binding affected across the chromosomes for WT and mutant?
4. Functional enrichment analysis for WT and mutant?

I will be using the ChIP-seq specific R Bioconductor packages to do my ChIP-seq analysis. 
```{r}
library(ChIPseeker)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
txdb <- TxDb.Hsapiens.UCSC.hg38.knownGene
library(clusterProfiler)
```

## Proposed Timeline & Major milestones (or segments).
Milestone 1 (11/14/2019): Get familiar with using the ChIPseeker package by working with a known data set. Try to get the result for the first two problems.
Milestone 2 (11/21/2019): Continue with understanding the package and answer the last two questions.
Milestone 3 (11/27/2019): Optimizing the results and overcome any road blocks hit. Submit a rough draft for QA. 
Milestone 4 (12/06/2019): Address the QA problems and make the final draft. Submit the final project.

## Milestone 2
I am still working with the ChiPseeker vignette with a known data set. I was able to answer the last two questions but I still have to work on them to look asthetically beautiful. I also have to work on the first two questions to look more beautiful. I am also trying to learn other features of ChiPseeker package.

## Loading files
```{r}
files <- getSampleFiles()
print(files)
files
peak <- readPeakFile(files[[4]])
peak
P1 <- data.frame(peak)
setwd("~/desktop/files/peaks")
f1 <- readPeakFile("IP-WT_S13_vs_Input-WT_S15_peaks.chrfiltered.bed")
f2 <- readPeakFile("IP-4RK_S16_vs_Input-4RK_S14_peaks.chrfiltered.bed")
f1
f2
wildtype <- data.frame(f1)
mutant <- data.frame(f2)
```

## Annotate peaks
```{r}
covplot(peak, weightCol="V5")
covplot(f1, weightCol="V5")
covplot(f2, weightCol="V5")
```

## Functional Enrichment plots
```{r}
library(ReactomePA)
peakAnno_wt <- annotatePeak(f1, tssRegion=c(-1000, 1000),
                         TxDb=txdb)
peakAnno_mutant <- annotatePeak(f2, tssRegion=c(-1000, 1000),
                         TxDb=txdb)

pathway_wt <- enrichPathway(as.data.frame(peakAnno_wt)$geneId)
head(pathway_wt, 2)
barplot(pathway_wt, title = "Runx2 WT")

pathway_mutant <- enrichPathway(as.data.frame(peakAnno_mutant)$geneId)
head(pathway_mutant, 2)
barplot(pathway_mutant, title = "Runx2 Mutant")
```

